%-------------------------
% Resume in Latex
% Author : Swapnil Dutta
% License : Unlicense
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
  \textbf{\Huge \scshape Swapnil Dutta} \\ \vspace{1pt}
  \href{mailto:swapnil@rycerz.es}{swapnil@rycerz.es} $|$
  \href{https://linkedin.com/in/swapnildutta1}{LinkedIn} $|$
  \href{https://github.com/rycerzes}{GitHub} $|$
  \href{https://rycerz.es}{rycerz.es}
\end{center}


%-----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Siemens}{Bengaluru, India}
{Research Engineer Intern}{Oct 2025 -- Present}
\resumeItemListStart
\resumeItem{Built an 18k+ row electronic-component analytics toolkit with semantic, keyword, and hybrid retrieval, plus a DuckDB + LLM chat interface for context-aware querying.}
\resumeItem{Built a scalable dataset pipeline with preprocessing and corrupt-sample filtering, supporting 20k-image YOLOE training and 200k-image companion MLLM runs for SLD object detection.}
\resumeItem{Fine-tuned YOLOE-26 for SLD detection as well as Rex-Omni (Qwen2.5-VL) training/evaluation for one-shot and zero-shot detection via text and visual prompts, using LoRA on RTX 4090.}
\resumeItem{Worked on a benchmark for evaluating 6D pose estimation models (SAM-6D, FoundationPose, GigaPose).}
\resumeItemListEnd

\resumeSubheading
{Puch AI}{Remote}
{AI Engineering Intern}{Sep 2025 -- Oct 2025}
\resumeItemListStart
\resumeItem{Architected an asynchronous OpenAI wrapper for a WhatsApp chatbot, implementing a robust tool-calling framework supporting 30+ integrated tools with intelligent fallback mechanisms.}
\resumeItem{Engineered a full observability suite using Sentry (error tracking), Langfuse (LLM traces), and PostHog (feature flags) to monitor conversation state and agent performance in real-time.}
\resumeItem{Built automated test suites for async workflows to ensure reliability across multi-step agent conversations.}
\resumeItemListEnd

\resumeSubheading
{Cosdata}{Remote}
{Software Engineering Intern (Rust/Vector Search)}{May 2025 -- Sep 2025}
\resumeItemListStart
\resumeItem{Extended a Vector Database engine by implementing Hybrid Search (Dense + Sparse) and batch processing endpoints in Rust (Actix Web), significantly improving retrieval flexibility.}
\resumeItem{Benchmarked retrieval performance using BEIR datasets against SOTA algorithms (DiskANN, HNSW), tracking QPS and CPU latency to guide core engine optimizations.}
\resumeItem{Implemented memory-efficient chunked streaming (200k vectors/chunk) and remote embedding caching (vLLM), reducing indexing overhead and latency.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS & OPEN SOURCE-----------
\section{Projects \& Open Source}
\resumeSubHeadingListStart
\resumeProjectHeading
{\href{https://github.com/meta-pytorch/openenv}{\textbf{Meta-PyTorch/OpenEnv}} $|$ \emph{Open Source Contributor}}{Nov 2025 -- Present}
\resumeItemListStart
\resumeItem{Designed and shipped WebSocket concurrency in OpenEnv with per-session environment factories and capacity controls, enabling concurrent rollouts without one container per episode.}
\resumeItem{Fixed MCP reliability by unifying HTTP/WebSocket session lifecycle and correcting \texttt{list\_tools}/\texttt{call\_tool} deserialization, removing state resets and validation failures.}
\resumeItem{Modernized developer experience by standardizing environment packaging with \texttt{pyproject.toml}+\texttt{uv}, migrating core models to Pydantic, and adding parameterized \texttt{reset}/\texttt{step} APIs.}
\resumeItemListEnd

\resumeProjectHeading
{\href{http://github.com/3xCaffeine/mcp-server}{VaultAssist MCP Server} $|$ \emph{MCP, OAuth 2.1, Google APIs}}{Aug 2025}
\resumeItemListStart
\resumeItem{Built a secure Model Context Protocol (MCP) server exposing 50+ Google Workspace tools through OAuth 2.1, utilizing graph-database-backed memory for cross-service context management in personal AI assistants.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/rycerzes/agent-memory}{Agent Memory System} $|$ \emph{Neo4j, ChromaDB}}{Jul 2025}
\resumeItemListStart
\resumeItem{Designed a hybrid memory framework combining vector search (ChromaDB) and knowledge graphs (Neo4j) to manage semantic and episodic memories, enabling AI agents to retain long-term context.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{KIIT University}{Bhubaneswar, India}
{B. Tech. in Computer Science and Engineering}{Graduation Date: Jun 2026}
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, SQL, Typescript, Bash, Rust} \\
        \textbf{Machine Learning}{: PyTorch, LoRA, Hugging Face, Diffusers, vLLM, post training (SFT/RL)} \\
        \textbf{LLM \& Agent Systems}{: LLMOps, MCP/Tool Calling, RAG, Agentic Loop, RL Environments} \\
        \textbf{Vision \& Robotics}{: YOLOE, Qwen2.5-VL, Rex-Omni, SAM-6D, FoundationPose, GigaPose} \\
        \textbf{Data \& Retrieval}{: Vector DBs, Hybrid Search (Dense + Sparse), chunking, embedding/reranking}
        }}
\end{itemize}

%-------------------------------------------
\end{document}